---
title: "hw02-Tianshu-Zhao"
author: "Tianshu Zhao"
date: "2017.10.1"
output:
  html_document: default
  github_document: default
---
Download the data
```{r}
# download csv file to your working directory
# (do NOT include this code in your Rmd)
setwd('C:/Users/ariel/Desktop')
github <- "https://github.com/ucb-stat133/stat133-fall-2017/raw/master/"
file <- "data/nba2017-player-statistics.csv"
csv <- paste0(github, file)
download.file(url = csv, destfile = 'nba2017-player-statistics.csv')
```
___Question 1___ Create a data dictionary

See the file 'nba2017-player-statistics-dictionary.md' in the 'data' folder in the 'hw02' dictorary.

___Question 2____  

Part I
```{r}
# read data as a format of  read.csv( ), and use str( ) to display its structure
data <- read.csv('C:/Users/ariel/Desktop/nba2017-player-statistics.csv',
        colClasses = c('character',
                       'character',
                       'factor',
                       'character',
                       'numeric',
                       rep('integer',19)))
data
str(data)
```
Part II
```{r}
# Create another data frame for the output of read_csv( ) and  use str() to check its structure
library(readr)
data_new<- read_csv('C:/Users/ariel/Desktop/nba2017-player-statistics.csv',
                    col_types = list(Player = col_character(), 
                                     Team = col_character(),
                                     Position = col_factor(c('C','PF','PF','SF','SG')),
                                     Experience = col_character(),
                                     Salary = col_double()))

data_new
str(data_new)
```

___Question 3___
Replace all the occurences of "R" with 0, and then convert the entire column into integers.
```{r}
Experience_int <- as.integer(replace(data$Experience,data$Experience == "R", 0))
Experience_int
```

___Question 4___  Performance of players
Create variable first 
```{r}
# Missed field goals = Field Goals Made - Field Goal Attempts
Missed_FG <- data$FGA- data$FGM
#Missed free throws
# Missed free throws = Free Throw Attempts = Free Throw made
Missed_FT <- data$FTA- data$FTM
#PTS (total points) = 2-Point field goal attempts -3-Point Field Goals 
PTS <- data$FTM +2 * data$Points2 +3*data$Points3
#REB(total rebounds: offiensive and defensive)
# offensive rebounds - Defensive rebounds
REB <- data$OREB +data$DREB
#MPG(minutes per game; Not to be used when calculating EFF)
#Minutes Played during regular season / Games Played furing regular season
MPG <- data$MIN / data$GP
```
Create EFF 
```{r}
#EFF = (PTS + REB + AST + STL +BLK - Missed FG - Missed FT -TO) / GP
# Only add data$EFF if the variable is in data frame
data$EFF <- (PTS + REB + data$AST + data$STL + data$BLK - Missed_FG - Missed_FT - data$TO) / data$GP
summary(data$EFF)
```

```{r}
# Create histogram for the EFF
hist(data$EFF,
     main = 'Histogram of Efficiency (EFF)',
     xlab = 'EFF',
     las = 1,
     col = 'blue')
```
Display the player name, team, salary, and EFF value of the top-10 players by EFF in
decreasing order (display this information in a data frame).
```{r}
library(dplyr)
#arrange to order dat by EFF
#select to select column
#slice to slice first 10 rows
slice(select(arrange(data,desc(data$EFF)),c('Player','Team','Salary','EFF')),1:10)
```
Provide the names of the players that have a negative EFF.
```{r}
library(dplyr)
select(filter(data, EFF<0),Player)
```
? Use the function cor() to compute the correlation coefficients between EFF and all the
variables used in the EFF 
? Notice that Missed_FG, Missed_FT, and TO contribute negatively to EFF, so make
sure to take into account this negative association when calculating the correlation
coefficients.
```{r}
# Rearrange correlation coefficients in decreasing order
correlation <- data.frame(PTS = cor(data$EFF, PTS), 
                          REB = cor(data$EFF,REB), 
                          AST = cor(data$EFF, data$AST),
                          STL = cor(data$EFF, data$STL),
                          BLK = cor(data$EFF, data$BLK),
                          Missed_FG = cor(data$EFF, - Missed_FG),
                          Missed_FT = cor(data$EFF, - Missed_FT),
                          TO = cor(data$EFF, - data$TO))
```

Display the sorted data frame
```{r}
correlation_s <- correlation[1, c(order(correlation[1, ], decreasing = TRUE))]
correlation_s
```

Draw the barplot of the data frame
```{r}
barplot(as.numeric(correlation_s), 
        ylim = c(-1, 1), 
        main = 'Correlations between Player Stats and EFF',
        names.arg = variable.names(correlation_s),
        col = ifelse(as.numeric(correlation_s) > 0,"grey","coral1"),
        border = NA,
        cex.names = 0.6)
abline(h = 0)
```

___Question 5___
produce a scatterplot between Efficiency
(x-axis) and Salary (y-axis), including a lowess smooth line (locally weighted scatterplot
smoothing).

```{r}
# Scatterplot between EFF and Salary
library(scales)
plot(data$EFF, data$Salary/1000000,
     main = 'Efficiency versa Salary (Million)',
     xlab = 'Efficiency',
     ylab = 'Salary in Million',
     las = 1,
     pch = 21,
     col = alpha('blue', 0.6),
     bg = alpha('red', 0.6))
# Lowess line
lines(lowess(data$EFF, data$Salary/1000000),
      col = 'green',
      lwd = 2)
# Correlation coefficient between them
cor(data$EFF, data$Salary/1000000)
  
```

So, the relationship between salary and efficiency are positive related.As the efficient of a player goes higher, the salary of player goes higher as well.


```{r}
# Add MPG to dat.
data<- mutate(data, MPG)
# Create a data frame with players with MPG >= 20.
players2 <- data[data$MPG >= 20, ]
# Create a scatterplot between Efficiency and Salary, including a lowess smooth line.
plot(players2$EFF, players2$Salary/1000000,
     main = 'Efficiency vs Salary (Million)',
     sub = 'For players with MPG >= 20',
     xlab = 'Efficiency',
     ylab = 'Salary (Million)',
     las = 1,
     pch = 21,
     col = alpha('blue', 0.6),
     bg = alpha('red', 0.6))

lines(lowess(players2$EFF, players2$Salary/1000000),
      col = 'green',
      lwd = 2)
# Compute the linear correlation coefficient between these variables.
cor(players2$EFF, players2$Salary)
```

According to the images above, the relationship between players' salary and efficiency are still positive.


___Question 6____

Q:What things were hard, even though you saw them in class/lab?
A:figure out the correct sequence of the syntax of the plots.
Q:What was easy(-ish) even though we haven’t done it in class/lab?
A: Google the things I don't know.
Q:Did you need help to complete the assignment? If so, what kind of help?
A: Kind of , I asked the GSI and my friends for help.
Q: How much time did it take?
A: About 5 hours, I spent very long time read and summarized the lecture slides.
Q: What was the most time consuming part?
A: Draw the plots.
Q: Was there anything that you did not understand? or fully grasped?
A: Somethings were perfectly run yesterday, but suddenly got some bugs when I woke up next day.
Q:Was there anything frustrating in particular?
A: Yes
Q:Was there anything exciting? Something that you feel proud of? (Don’t be shy, we
won’t tell anyone).
A: No



