---
title: "Stat133 HW1"
author: "Tianshu Zhao"
date: "2017.9.22"
output: github_document
---

```{r}
# load nba data set first
load("nba2017-salary-points.RData")
# List the avaiable objects
ls()
```

___Question 1: A bit of data preprocessing____
# 1) convert the measurement sacle of data

```{r}
# create a new salary measured in millions of dollars, up tp 2 decimal digits
salary_million <- as.numeric(round(salary/1000000,2),nsmall <- 2)

salary_million

```
# 2) The variable experience is a character vector. If you take a look at its elements, you
will see that there are numbers as well as the character "R". The character "R" means
that the player is a rookie (i.e. first season playing in the NBA). Replace the values
"R" by "0", and create a new experience variable as an integer vector.
```{r}
# create a new experience variable as an integer vector
experience_integer <- as.integer(replace(experience,experience == "R",0))
```

# 3) The variable position is a character vector. Create a new position variable as an R
factor (see ?factor). Provide more descriptive labels for the factor’s levels (i.e. the
categories), for instance:? 'center' instead of "C"
? 'small_fwd' instead of "SF"
? 'power_fwd' instead of "PF"
? 'shoot_guard' instead of "SG"
```{r}
# Create a new position variable as R factor
position_factor <- factor(position)
position_factor
#Provide more descriptive labels for the factor's levels
levels(position_factor) <- c("center","small_fwd","power_fwd","shoot_guard","point_guard")

#Compute the frequencies (number of occurences) with the function table( )
table(position_factor)
```


___Question 2____Scatterplot of Points and Salary____
```{r}
# Scatterplot of Points and Salary
plot(points,salary_million,xlab = "points",ylab = "salary_million",pch = 0, col = "blue", cex = 0.5, main ="scatterplot of Points and Salary")
```


___Qustion 3 Correlation between Points and Salary___

```{r}
n <- 441
x_bar_mean <- sum(points)/n
x_bar_mean
y_bar_mean <- sum(salary_million)/n
y_bar_mean
var_x <- sum((points - x_bar_mean)^2)/(n-1)
var_x
var_y <- sum((salary_million - y_bar_mean)^2)/(n-1)
var_y
sd_x <- sqrt(var_x)
sd_x
sd_y <- sqrt(var_y)
sd_y
cov_xy <- sum((points - x_bar_mean)*(salary_million - y_bar_mean))/(n-1)
cov_xy
corr_xy <- cov_xy/((sd_x)*(sd_y))
corr_xy
```

__Question 4 Simple Linear Regression___
#Create objects for:
#5
#??? b1 the slope term
#??? b0 the intercept term
#??? ?? Y the vector of predicted values (¡°y-hat¡±)

```{r}
b1 <- corr_xy*(sd_y/sd_x)
b0 <- y_bar_mean -b1*x_bar_mean
y_hat <- b0+b1*(points)
y_hat
```

Summary statistics (use summary()) of ?? Y .
```{r}
# summary statistics of y_hat
summary(y_hat)
```
*What is the regression equation? Use inline code to write the equation.
----'y_hat <- b0+b1*(points)'
*How do you interpret the slope coefficient b1?
----Regression coefficients represent the changes of the predictor variable per unit according to the means differences. Basically, it means that RC reflects the change based on one condition changes while the other conditions remain the same.
*How do you interpret the intercept term
When all the x interpret is zero, the expected mean value of Y is the intercept.


What is the predicted salary for a player that scores:
```{r}
# player scores
b0+b1*(c(0,100,500,1000,2000))
```



___Question 5 Plotting the regression line___
```{r}
plot(points,salary_million, xlab = "points", ylab = "salary_million", pch = 0, col = "purple", cex = 0.5, main = "Scatterplot of Points and Salary")
abline(b0, b1, lwd=1.5, col="purple")
lines(lowess(points, salary_million), lwd = 1.5, col = "red")
text(2300, 28, labels = "lowess", col = "red")
text(2300, 19, labels = "regression", col = "purple")
```



___Question 6 Regression residuals and Coefficient of Determination R^2___
```{r}
ei <- salary_million - y_hat
RSS <- sum((ei)^2)
TSS <- sum((salary_million - y_bar_mean)^2)
RR <- 1- RSS/TSS
RR
```

___Question 7 Exploring Position and Experience____
A scatterplot of Years-of-Experience and Salary, including a lowess smooth line (locally
weighted scatterplot smoothing).
```{r}
# A scatterplot of Years of Experience and Salary
plot(experience_integer, salary_million, xlab = "years_of_experience", ylab = "salary_million", pch = 21, col = "grey", cex = 1.5, main = "Scatterplot with lowess smooth")
# A lowess smooth line
lines(lowess(experience_integer, salary_million), lwd = 2.5, col = "red")
```
Use the function scatterplot3d() from the homonym package "scatterplot3d" to
create a 3D-scatterplot of Points, Experience, and Salary. Use Points for the x-axis,
Experience for y-axis, and Salary for the z-axis.
```{r}
# create a SD-scatterplot of Points ,Experience, and salary
library(scatterplot3d)
scatterplot3d(points, experience_integer,salary_million,main = "3D Scatterplot", xlab = "points", ylab="experience",zlab = "salary",
              color = "pink", pch = 21, asp = 80, las = 1)
```

```{r}

# A condition boxplot of Salary in terms of Position
boxplot(salary_million~position_factor,xlab = "position", ylab = "salary_million", las = 1)
```
*Provide concise descriptions for the plots of this section.
---- The line above he box represents the greatest value excluding utliers, the upper line of the box represents 25% of data greater than this value. The black line in the box means 50% of the data is greater than the value.
The lower line of the box represents the 25% of data less than his value.
The lowest line represents the least data value

*From the scatterplots, does Experience seem to be related with Salary? 
---- Yes, the more the experiences one player has, the more salary he gets.

*From the boxplot, does Position seem to be related with Salary?
---- No, According to the data shows above, the position and salary is irrealted.










____Question 8_____
1.What things were hard, even though you saw them in class?
----Fix the bugs.
2.What was easy(-ish) even though we haven¡¯t done it in class?
----Search the known code in google.
3.If this was the first time you were using git, how do you feel about it?
----It really really confusing and do never use git in Windows.
4.If this was the first time using GitHub, how do you feel about it?
----I feel ok for right now.
5.Did you need help to complete the assignment? If so, what kind of help? Who helped you?
----I joined a stat133 study group, and we did the homework together.I also asked GSI for help and hint.
6.How much time did it take to complete this HW?
----About 3 hours
7.What was the most time consuming part?
----I can not remember what is the exact command, the searching and finding the command code takes me most of the time.
8.Was there anything that you did not understand? or fully grasped?
Something a little bit, but I think I understand most of the part.
9.Was there anything frustrating in particular?
No
10.Was there anything exciting? Something that you feel proud of? (Don¡¯t be shy, we
won¡¯t tell anyone).

No
  








